Adopting agile in the large: motivations, success factors and challenges

### 2013-11-27 journal/article.tex
Corrected table captions
Review of code families

Agile practice & Agile practice or methodology used (eg. Scrum, XP) \\

@@

Geographical\newline location & Where the organization is located. Includes
headquarters and multisite locations. \\

@@

Measuring results of\newline transformation & Mentioning of how
transormation progress is measured, or how previous indicators have changed. \\

Satisfaction in agile & Internal or external satisfaction/trust/credibility is
mentioned. \\

Multisite / GSD & Mentioning of a multisite organization. This does not imply
that the multisite environment has brought special viewpoints on the agile
implementation. \\

@@

        \bottomrule
    \end{tabular}
    \caption{Context information}
    \label{table:codefamilies}
\end{table}

@@

The total accumulated codes and quotes of the integrated deductive and inductive
coding process are presented in Table \ref{table:codecount}.

\begin{table}[h]
    \begin{tabular}{ l r r }
        \toprule
        Code family    &  Codes  &  Quotes
        \\
        \midrule
        RQ1: Reason to change &        10 &   70 \\
		RQ2: Transformation process &  13 &  538 \\
		RQ3: Challenges &              39 &  307 \\
		RQ3: Success factors &         44 &  247 \\
		Investing in change  &          5 &  130 \\
		Practices &                    11 &  160 \\
		Other &                        11 &  194 \\
		Total &                       133 & 1440\footnotemark[2]
		\\
        \bottomrule
    \end{tabular}
    \caption{Context information}
    \label{table:codecount}
\end{table}

\footnotetext[2]{Due to technical reasons a small number of ``free quotations''
is included.}

>>>>

Agile method & Agile methods used in the organization (eg. Scrum, XP) \\

@@

Geographical\newline location & Where the organization is located. \\

@@

Multisite / GSD & Mentioning of a multisite organization. \\

@@

        \bottomrule
    \end{tabular}
    \caption{Code families}
    \label{table:codefamilies}
\end{table}

@@

The total accumulated codes and quotes of the integrated deductive and inductive
coding process are presented in Table \ref{table:codecount}. The total number of
quotations is less than the sum of quotations in the categories because a single
quotation may have multiple codes.

\begin{table}[h]
    \begin{tabular}{ l r r }
        \toprule
        Code family    &  Codes  &  Quotations
        \\
        \midrule
        RQ1: Reason to change &        10 &   70 \\
		RQ2: Transformation process &  13 &  538 \\
		RQ3: Challenges &              39 &  307 \\
		RQ3: Success factors &         44 &  247 \\
		Investing in change  &          5 &  130 \\
		Practices &                    11 &  160 \\
		Contextual &                    8 &  167 \\
		Total &                       133 & 1440 \\
        \bottomrule
    \end{tabular}
    \caption{Number of codes and quotations per code family}
    \label{table:codecount}
\end{table}
